---
title: "SamsungPhoneCleanFile"
author: "vz415"
date: "August 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load up the data by using list.files and merging the wanted files into a single dataframe
setwd("/Users/vincent_zaballa/Documents/Springboard Data Program/Section 3 Data Wrangling/SamsungPhoneDataCleaning")
file.list <- list.files()
data <- read.table()

# explore the data
str(data)
head(data)

# Convert into a local data frame
data <- tbl_df(data)

# Load dplyr and tidyr packages to help tidy up the datasets.
library("dplyr")
library("tidyr")
```

## Samsung Phone Data Wrangling Exercise

You should create one R script called run_analysis.R that does the following.

1. Merges the training and the test sets to create one data set.

2. Extracts columns containing mean and standard deviation for each measurement (Hint: Since some feature/column names are repeated, you may need to use the make.names() function in R)

3. Creates variables called ActivityLabel and ActivityName that label all observations with the corresponding activity labels and names respectively

From the data set in step 3, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}
# Merge training and test sets

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
