---
title: "SamsungPhoneCleanFile"
author: "vz415"
date: "August 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load dplyr and tidyr packages to help tidy up the datasets.
library("dplyr")
library("tidyr")
library("data.table")
library("plyr")
# Load up the data by using list.files and merging the wanted files into a single dataframe
setwd("/Users/vincent_zaballa/Documents/Springboard Data Program/Section 3 Data Wrangling/SamsungPhoneDataCleaning/UCI HAR Dataset/")

# Variable names from the features.txt file
vars_names <- read.table("features.txt", colClasses = c("NULL",NA))

# Specify file paths using file.path
# Test Data - subject test, x test, and y test
test_file_subject_test <- read.table(file.path("test", "subject_test.txt"), col.names = "Subject")
test_file_X_test <- read.table(file.path("test", "X_test.txt"), col.names = t(vars_names))
# Name the function done "ActivityLabel"
test_file_y_test <- read.table(file.path("test", "y_test.txt"), col.names = "ActivityLabel")

# Test Data - one leve down and reading in all the data with acc & gyro
test_file_Inertial_Signals <- file.path("test", "Inertial Signals", c("body_acc_x_test.txt",  "body_acc_y_test.txt",  "body_acc_z_test.txt", 
"body_gyro_x_test.txt", "body_gyro_y_test.txt", "body_gyro_z_test.txt",
"total_acc_x_test.txt", "total_acc_y_test.txt", "total_acc_z_test.txt"))
# test_signals <- lapply(test_file_Inertial_Signals, read.table) -> Not really necessary, just raw cumbersome data

# Repeat for training data
# Train Data - subject train, x train, and y train
train_file_subject_test <- read.table(file.path("train", "subject_train.txt"), col.names = "Subject")
train_file_X_test <- read.table(file.path("train", "X_train.txt"), col.names = t(vars_names))
# Name function "ActivityLabel"
train_file_y_test <- read.table(file.path("train", "y_train.txt"), col.names = "ActivityLabel")

# Train Data - one leve down and reading in all the data with acc & gyro
train_file_Inertial_Signals <- file.path("train", "Inertial Signals", c("body_acc_x_train.txt",  "body_acc_y_train.txt",  "body_acc_z_train.txt", 
"body_gyro_x_train.txt", "body_gyro_y_train.txt", "body_gyro_z_train.txt",
"total_acc_x_train.txt", "total_acc_y_train.txt", "total_acc_z_train.txt"))
# train_signals <- lapply(train_file_Inertial_Signals, read.table) -> Also no necessary.

# Alright, so for the features, the data is within the files and the featurename is the file name... Need to figure out how to add together the file's data and then make a column name with the file's title. So, 9 measurements have 128 variables with 2947 observations.

```

## Samsung Phone Data Wrangling Exercise

You should create one R script called run_analysis.R that does the following.

1. Merges the training and the test sets to create one data set.

  - Merge test_file_subject_test and train_file_subject_test : This is the file that specifies which volunteer. What does that even mean? 
  - Merge test_file_X_test and train_file_X_test
  - Merge test_file_y_test and train_file_y_test
  - Merge train_signals and test_signals
  - Finally, after understanding how they all come together, merge the appropriate rows/columns
  - Also, need to create an algorithm that counts the number of unique test subjects. 
  - Order doesn't really matter for this type of operation. Just need to concatenate the participants. Theoretically, order could matter if there was an error in the experimental methods of the experiment, but I'll come back to this later... Make an algorithm to sort which vector has the higher patient value and then switch to the lower number. 

2. Extracts columns containing mean and standard deviation for each measurement (Hint: Since some feature/column names are repeated, you may need to use the make.names() function in R)

  - From the blog post about this data:  "Ah yes, but you only want certain columns. Well, either a good educated guess or reading some of the other information files will point you towards which columns contain mean and standard deviation values. What R functions do you know that can find text patterns in character vectors? Can you think how to use the output of such a function to give you a way to select only certain columns?"
  - More wisdom: "Can you find the file that codes which observation is associated with particular subjects? And the file that codes which observation is associated with a particular activity?" Working on it.

```{r}
# Combining datasets to make one dataframe. First combining training and test data by rows.
X_tests <- bind_rows(test_file_X_test, train_file_X_test)
y_tests <- bind_rows(test_file_y_test, train_file_y_test)
subject_tests <- bind_rows(test_file_subject_test, train_file_subject_test)
# Combining the columns
Compiled_higherdata <- bind_cols(X_tests, y_tests, subject_tests)

# Start by tracking indices of subjects.
unique_subjects_indices <- row(unique(subject_tests), as.factor = T)
numeric_subjects_indices <- as.numeric(levels(unique_subjects_indices))[unique_subjects_indices]

# Identify only the columns with mean or stddev. Start by finding indices of vars_names
mean_indices <- which(as.character(grepl(".mean.", vars_names[,1])) == "TRUE")
Mean_indices <- which(as.character(grepl(".Mean.", vars_names[,1])) == "TRUE")
std_indices <- which(as.character(grepl(".std.", vars_names[,1])) == "TRUE")
vars_indices_keep <- sort(c(mean_indices, std_indices, Mean_indices))
# Apply to original dataset, but remember to keep ActivityLabel, ActivityName and subject columns (562 & 563)
Compiled_higherdata <- Compiled_higherdata[,c(vars_indices_keep, 562, 563)]

```

## Creating variables ActivityLabel and ActivityName

3. Creates variables called ActivityLabel and ActivityName that label all observations with the corresponding activity labels and names respectively

4. From the data set in step 3, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

Thoughts: "Can you find the file that codes which observation is associated with particular subjects? And the file that codes which observation is associated with a particular activity? Obviously in both cases, the files you're looking for will have the same length as the number of observations. How do you now combine them with your data (measurement) data frame? And how do you interpret the activity, which is just a number? We want something more meaningful. Which file relates activity number to its label/description? Can you now use this to add a new column that has the appropriate activity label?" 

```{r}
# Convert the tests from numbers to descriptive factors that will be used for ActivityNames. Use ifelse statements and mutate. 
Compiled_higherdata <- mutate(Compiled_higherdata, ActivityName =
  ifelse(Compiled_higherdata$Activity == "1", "Walking", 
  ifelse(Compiled_higherdata$Activity == "2", "Walking_Upstairs", 
  ifelse(Compiled_higherdata$Activity == "3", "Walking_Downstairs",
  ifelse(Compiled_higherdata$Activity == "4", "Sitting", 
  ifelse(Compiled_higherdata$Activity == "5", "Standing", 
  ifelse(Compiled_higherdata$Activity == "6", "Laying", "NA")))))))

# Create independent tidy data set with the average of each variable for each activity and subject. To do this, going to compress all activities for each subject and output the average of that value. 


```

## Future Work

The following code will match the subject with each test performed. Will know when they were performing each task and for how long. Good for future analysis. 

```{r}
# Make a loop that finds and lists the number and types of tests performed on each subject. Do this Section later later.

# Ok, can use the duplicated function to find duplicates. To solve the problem of mutliple tests, can use an if statement that says that "if 6 duplicates have been found, restart the duplicate search at the next number" Just need to figure out how to go to the next number from the last duplicate. Know this should only be performed twice. Find indices. 
for (i in 1:(length(numeric_subjects_indices) - 1)) {
  subject_y_test <- numeric_subjects_indices[i+1]
  # Below are ideas of what to do to find subject_y_test
  which(duplicated(y_tests[1:(303)-1,]) == F ) # indices output
  adply(y_tests[i:(i+1)-1,])
  subj_test_index[(2 * i - 1),] <- y_tests[numeric_subjects_indices[i] + c( which( duplicated( y_tests[numeric_subjects_indices[i] : (numeric_subjects_indices[i+1]-1),]) == F )),]
  next # Use this once the first iteration of unique indices has been found
  subj_test_index[(2 * i),] <- y_tests[ numeric_subjects_indices[i] + c( which( duplicated( y_tests[ numeric_subjects_indices[i]: (numeric_subjects_indices[i+1]-1),]) == F )),]
}   # What is the output going to be? A vector indicating the indices of the which subject performed which test, maybe. Know the output will be "5 4 6 1 3 2", so maybe there's an easier way than trying to geuss the middle point of the range.


# Find the indices for tests performed by each subject. Need to apply for loop that repeats unique locations for each test for each subject.
unique_rows <- function (uniques) {
  row(unique(uniques), as.factor = T)
}

# First attempt at finding the unique test that a patient performed.
unique_subjtests <- lapply(y_tests, unique_rows)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
