---
title: "SamsungPhoneCleanFile"
author: "vz415"
date: "August 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load up the data by using list.files and merging the wanted files into a single dataframe
setwd("/Users/vincent_zaballa/Documents/Springboard Data Program/Section 3 Data Wrangling/SamsungPhoneDataCleaning/UCI HAR Dataset/")
# Specify file paths using file.path
# Test Data - subject test, x test, and y test
test_file_subject_test <- read.table(file.path("test", "subject_test.txt"))
test_file_X_test <- read.table(file.path("test", "X_test.txt"))
test_file_y_test <- read.table(file.path("test", "y_test.txt"))
# Test Data - one leve down and reading in all the data with acc & gyro
test_file_Inertial_Signals <- file.path("test", "Inertial Signals", c("body_acc_x_test.txt",  "body_acc_y_test.txt",  "body_acc_z_test.txt", 
"body_gyro_x_test.txt", "body_gyro_y_test.txt", "body_gyro_z_test.txt",
"total_acc_x_test.txt", "total_acc_y_test.txt", "total_acc_z_test.txt"))
test_signals <- lapply(test_file_Inertial_Signals, read.table)

# Repeat for training data
# Train Data - subject train, x train, and y train
train_file_subject_test <- read.table(file.path("train", "subject_train.txt"))
train_file_X_test <- read.table(file.path("train", "X_train.txt"))
train_file_y_test <- read.table(file.path("train", "y_train.txt"))
# Test Data - one leve down and reading in all the data with acc & gyro
train_file_Inertial_Signals <- file.path("train", "Inertial Signals", c("body_acc_x_train.txt",  "body_acc_y_train.txt",  "body_acc_z_train.txt", 
"body_gyro_x_train.txt", "body_gyro_y_train.txt", "body_gyro_z_train.txt",
"total_acc_x_train.txt", "total_acc_y_train.txt", "total_acc_z_train.txt"))
train_signals <- lapply(train_file_Inertial_Signals, read.table)

# Alright, so for the features, the data is within the files and the featurename is the file name... Need to figure out how to add together the file's data and then make a column name with the file's title

# Function to process each file
processFile <- function(f) {
  df <- read.csv(f)
  # ...and do stuff...
  file.info(f)$size # dummy result
}

# Find all .csv files
files <- dir("/foo/bar/", recursive=TRUE, full.names=TRUE, pattern="\\.csv$")

# Apply the function to all files.
result <- sapply(files, processFile)

# Convert into a local data frame
data <- tbl_df(data)

# Load dplyr and tidyr packages to help tidy up the datasets.
library("dplyr")
library("tidyr")
```

## Samsung Phone Data Wrangling Exercise

You should create one R script called run_analysis.R that does the following.

1. Merges the training and the test sets to create one data set.

2. Extracts columns containing mean and standard deviation for each measurement (Hint: Since some feature/column names are repeated, you may need to use the make.names() function in R)

3. Creates variables called ActivityLabel and ActivityName that label all observations with the corresponding activity labels and names respectively

From the data set in step 3, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}
# Merge training and test sets

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
